---
title: "Product Specific Insurance"
output:
  html_document:
    df_print: paged
    toc: yes
---

Contained in this notebook is the product specific insurance simulation

# Setting up

We first import libraries, which are only used in the visualisation of our results.

```{r}
library(ggplot2)
library(dplyr)
```

As required, we first set the seed to 1, for re-producability of our results. 

```{r}
set.seed(1)
```


# Function Definitions

We define the following function to generate the next event time after t in a homogeneous Poisson process

```{r}
#The function takes in current time t and intensity x
next_pois <- function(t, x) {
  
  #Generates random uniform variable
  U <- runif(1)
  
  #Returns the next time, following formula for Poisson process
  return(t - (1/x) * log(U)) 
}
```

The next two functions are the building blocks for the non-homogeneous Poisson process. We first define mu_t to calculate the rate of the process, and next_dep generates the next time after t in the process.

```{r}
#The function takes in current time t
mu_t = function(t){
  
  #Calculates intensity using formula given in brief
  return(1/(t+12))
}
```

```{r}
#The function takes in current time t and max possible mu
next_dep <- function(t, mu) {
  
  #Sets flag for the while loop so it runs
  flag = 1
  
  while(flag){
    
    #Generates random uniform variable
    U1 <- runif(1)
    
    #Calculates next event time in process
    t = t - (1/mu) * log(U1)
    
    #Generates a second random uniform variable
    U2 <- runif(1)
    
    #Calculates the rate, and checks if it satisfies requirement for non-homogeneous process
    if (U2 <= mu_t(t)/mu) {
      
      #Sets time to t
      T_s <- t
      
      #Breaks while loop
      flag = 0
    }
  }
  
  #Returns the calculated next event time t
  return (T_s)
}
```

We next define a function that allows us to track which months we are in. The function checks if the month is in our tracking list, and returns true if it inst, and false otherwise.


```{r}
#Takes in current time and current month list
new_month <- function(t, months) {
  
  #If the floor of the current t is not in the months list
  if (floor(t) %in% months) {
    
    #Returns false
    return(FALSE)
    
  } else {
    
    #Returns true 
    return(TRUE)
  }
}
```

We next define a function to update the sample mean and variance. We use the formulas outlined in the lectures

```{r}
#Takes in current iteration, current mean, current sample mean, current sample variance
gen_sample_mean_var = function(n, Z, Z_bar, S_sq){
  
  #Calculates new sample mean
  Z_bar_new = Z_bar + (Z-Z_bar)/(n+1)
  
  #Calculates new sample variance
  S_sq_new = (1-(1/n))*S_sq + (n+1)*(Z_bar_new - Z_bar)^2
  
  #Returns our calculated variables
  return(c(Z_bar_new,S_sq_new))
}
```

# Simulation 

We are first given some parameters, which are initialized below

```{r}
#Monthly poisson process parameter for arrivals
lambda <- 3

#Monthly non-homogeneous Poisson process rate, since this is the max mu_t can attain
mu <- 1/12

#Yearly poisson process parameter for claims
alpha <- 3.5

#Starting capital
c_0 <- 50000

#Capital floor
C <- 30000
  
#Fixed monthly fee
M <- 300
```


```{r}
### Output Variables ################################

#Output variable to record iteration at which we have our required estimator
k_90 <- 0

#Output variable to record the required estimate
C_12_90 <- 0

#Output variable to record the standard deviation of our estimator
S_sq_90 <- 0

#Defines list to record each C_12, used for plot
capital_list <- c()

### Other Initialisations ############################

#We need to initialise the first variance, that being 0
S_sq <- 0

#And the start of the counter
k <- 1



### Main Loop ########################################

#We next define a while loop, so we run the simulation for 3000 iterations.

while (k < 3000) {
  
### Starting Parameters #################
  
  #Start at time 0
  t <- 0
    
  #Number of arrivals by time t
  n_A <- 0
  
  #We run simulation for 12 months
  total_t <- 12
  
### State variables ######################
  
  #Number of customers currently in system
  n_0 <- 0
  
  #Defines our current cost accrued
  cost <- 0
  
  #Defines our current revenue generated
  rev <- 0
  
  #Describes what month we are currently in
  months <- c()
  
### Event variables ######################
  
  #Define time of next arrival from Poisson process 
  t_A <- next_pois(t, lambda)
  
  #Define list of next departures
  t_D <- c(Inf)
  
  #Define list of next claims
  t_C <- c(Inf)
  
### 12 Month Loop ########################

  while(t <= total_t){
    
    #Calculate whether we are in new month yet
    if (new_month(t, months)) {
      
      #If yes, then add month to list
      months <- c(months, floor(t))
      
      #then add monthly income to revenue
      rev <- rev + M*n_0
    }
    
    #If there is arrival
    if ((all(t_A <= t_D)) & (all(t_A <= t_C))){
      
      #Set time to time of next arrival
      t <- t_A
      
      #Add arrival to number of arrivals
      n_A <- n_A + 1
      
      #Count arrival in system count
      n_0 <- n_0 + 1
      
      #Calculate next arrival time
      t_A <- next_pois(t, lambda)
      
      #We calculate time to next claim for this customer
      #We index the list by the number arrival they are
      t_C[n_A] <- next_pois(t, (alpha/12))
      
      #we need to calculate next departure time for this customer
      #We again index list by the number of arrival they are
      t_D[n_A] <- next_dep(t, mu)
      
    }
    
    #If there is a departure
    else if (any(t_D < t_A) & any(t_D < t_C)) {
      
      #Set time to time of next departure
      t <- min(t_D)
      
      #Subtract departure from system count
      n_0 <- n_0 - 1
      
      #Set this customers departure time to infinity, since they have now left
      t_D[which.min(t_D)] <- Inf
      
      #Set this customers next claim time to infinity, since they have now left
      t_C[which.min(t_D)] <- Inf

    }
    
    #If there is a claim
    else if (any((t_C < t_A)) & any((t_C < t_D))){
      
      #Set time to time of next claim
      t <- min(t_C)
  
      #Generate next claim time for this customer
      t_C[which.min(t_C)] <- next_pois(t, (alpha/12))
      
      ## Calculate pay-out ##
      
      #Generate random uniform variable
      pay_out_p <- runif(1)
    
      #If the variable is less than 0.6, then execute code
      if (pay_out_p <= 0.6){
        
        #Calculate random variable, multiply by 10, and obtain its upper integer 
        X <- ceiling(10*runif(1))
        
        #Calculate pay-out based on this
        pay_out <- 300*X + 500
        
        #Add it to the running total
        cost <- cost + pay_out
      }
    }
    
  }
  
  ## Estimation of C_12 ##
  
  #We first calculate our simulated capital at the end of 12 months
  C_12 <- (c_0 - cost + rev)
  
  #Add it to the list of C_12s
  capital_list <- c(capital_list, C_12)
  
  #If it is the first iteration, we set the sample mean to our first estimate
  if (k == 1){
    
    #Set it equal to the first calculated C_12
    C_12_bar <- C_12
  }
  
  #We now generate our next sample mean and variance
  out <- gen_sample_mean_var(k, C_12, C_12_bar, S_sq)
  
  #We then retrieve these values
  C_12_bar <- out[1]
  S_sq <- out[2]
  
  #We then print this to assess convergence (Used only for diagnostics)
  #print(sqrt(S_sq/k))
  
  #We then check we have satisfied our requirements for confidence interval, the last condition
  #ensures we record only the first time we satisfy this requirement
  
  if (sqrt(S_sq/k) < (500/1.645) & k != 1 & (C_12_90+k_90+S_sq_90 == 0)){
    
    #We then collect our output values
    C_12_90 <- C_12_bar
    k_90 <- k
    S_sq_90 <- S_sq
  }
  
  #We then add to counter
  k <- k+1
  
}
```

# Output Analysis

## Estimation of `C_12`

We first want an acceptable d, so we calculate d = (500/1.645), Assuming CLT applies.

Thus, we have we run the loop until:

$$ \frac{S}{\sqrt{k}} < \frac{500}{1.645}$$

where S is the standard deviation up until that iteration, and k is the iteration.

We next estimate the capital we finish with, if we retrieve our output variable C_12

```{r}
#Prints our output variables
C_12_90
k_90
S_sq_90 
```
From here, we calculate our final standard deviation

```{r}
#Calculates standard deviation
S_90 <- sqrt(S_sq_90/k_90)
S_90
```

So we on the 2034th iteration, we achieved our estimate of 32585.55. Our estimator has a standard deviation of 303.8578.

From here, we use the z-score of 1.96 to calculate an interval that we can be 95% our true value is in. With our standard deviation of 303.8578, we find calculate 1.96*303.8578. So our interval is +/- 595.5612.

## Distribution Visualisation 

We now wish to visual the distribution of C_12s using our capital_list

```{r}
#First calculate frequencies at which each C_12 occurred
freq <- data.frame(list(capital_list))
```

```{r}
#Define plot
plot_1 <- ggplot(freq, aes(x = capital_list)) +
  
    #Set to histogram and change colour
    geom_histogram(bins = 70, fill = "#00BFC4") +
  
    #Change axes labels
    xlab("Capital Stock at 12 Months") +
    ylab("Simulations") +
  
    #Add C line
    geom_vline(xintercept=30000)

#Print plot
plot_1
```

