---
title: "Product Specific Insurance"
output:
  html_document:
    df_print: paged
    toc: yes
---

Contained in this notebook is the product specific insurance simulation

We first import libraries, which are only use in the visualisation of our results.

```{r}
library(ggplot2)
library(dplyr)
```

As required, we first set the seed to 0, for re-producability of our results. 

```{r}
set.seed(1)
```

# Function Definitions

```{r}
next_pois <- function(t, x) {
  U <- runif(1)
  return(t - (1/x) * log(U)) 
}
```

```{r}
mu_t = function(t){
  return(1/(t+12))
}
```

```{r}
next_dep <- function(t, lambda) {
  flag = 1
  while(flag){
    U1 <- runif(1)
    t = t - (1/lambda) * log(U1)
    
    U2 <- runif(1)
    
    if (U2 <= mu_t(t)/lambda) {
      T_s <- t
      flag = 0
    }
  }
  
  return (T_s)
}
```

```{r}
new_month <- function(t, months) {
  if (floor(t) %in% months) {
    return(FALSE)
  } else {
    return(TRUE)
  }
}
```

```{r}
gen_sample_mean_var = function(n, Z, Z_bar, S_sq){
  
  Z_bar_new = Z_bar + (Z-Z_bar)/(n+1)
  
  S_sq_new = (1-(1/n))*S_sq + (n+1)*(Z_bar_new - Z_bar)^2
  
  return(c(Z_bar_new,S_sq_new))
}
```

# Simulation 

We are first given some parameters, which are initialized below

```{r}
#Monthly poisson process parameter for arrivals
lambda <- 3

#Yearly poisson process parameter for claims
alpha <- 3.5

#Starting capital
c_0 <- 50000

#Capital floor
C <- 30000
  
#Fixed monthly fee
M <- 300
```


```{r}
### Output Variables ################################

k_90 <- 0 
C_12_90 <- 0
S_sq_90 <- 0

capital_list <- c()

### Other Initialisations ############################

#We need to initialise the first variance, that being 0

S_sq <- 0

#And the start of the counter
k <- 1



### Main Loop ########################################

#We next define a while loop, so we run the simulation for 3000 iterations.

while (k < 3000) {
  
### Starting Parameters #################
  
  #Start at time 0
  t <- 0
    
  #Number of arrivals by time t
  n_A <- 0
  
  #Number of departures by time t
  n_D <- 0
  
  #Number of claims by time t
  n_C <- 0
  
  #We run simulation for 12 months
  total_t <- 12
  
### State variables ######################
  
  #Number of customers currently in system
  n_0 <- 0
  
  #Defines our current cost accrued
  cost <- 0
  
  #Defines our current revenue generated
  rev <- 0
  
  #Describes what month we are currently in
  months <- c()
  
### Event variables ######################
  
  #Define time of next arrival from Poisson process 
  t_A <- next_pois(t, lambda)
  
  #Define time of next departure
  t_D <- Inf
  
  #Define list of next claims
  t_C <- c(Inf)
  
### 12 Month Loop ########################

  while(t <= total_t){
    
    #Here we check we have not entered a new month yet
    if (new_month(t, months)) {
      months <- c(months, floor(t))
      rev <- rev + M*n_0
    }
    
    #If there is arrival
      
    if ((t_A <= t_D) & (all(t_A <= t_C))){
      
      #Set time to time of next arrival
      t <- t_A
      
      #Add arrival to number of arrivals
      n_A <- n_A + 1
      
      #Count arrival in system count
      n_0 <- n_0 + 1
      
      #Calculate next arrival time
      t_A <- next_pois(t, lambda)
      
      #On first iteration, we now calculate time to next claim
      t_C[n_A] <- next_pois(t, (alpha/12))
      
      #On first iteration, we need to calculate next departure time
      if (n_A == 1) {
        t_D <- next_dep(t, lambda)
      }
      
    }
    
    #If there is a departure
    
    else if ((t_D < t_A) & all((t_D < t_C))) {
      
      #Set time to time of next departure
      t <- t_D
      
      #Subtract departure from system count
      n_0 <- n_0 - 1
      
      #Add departure to departure count
      n_D <- n_D + 1
      
      #Calculate next departure
      t_D <- next_dep(t, lambda)
    }
    
    #If there is a claim
    
    else if (any((t_C < t_A)) & any((t_C < t_D))){
      
      #Set time to time of next claim
      t <- min(t_C)
      
      #Add one claim to claim count
      n_C <- n_C+1
  
      #Generate next claim time
      t_C[which.min(t_C)] <- next_pois(t, (alpha/12))
      
      ##Calculate pay-out 
      
      #Generate random uniform variable
      pay_out_p <- runif(1)
    
      #If the variable is less than 0.6, then execute code
      if (pay_out_p <= 0.6){
        
        #Calculate random variable, multiply by 10, and obtain its upper integer 
        X <- ceiling(10*runif(1))
        
        #Calculate pay-out based on this
        pay_out <- 300*X + 500
        
        #Add it to the running total
        cost <- cost + pay_out
      }
    }
  }
  
  ### Estimation Section ###
  
  #We first our simulated capital at the end of 12 months
  C_12 <- (c_0 - cost + rev)
  capital_list <- c(capital_list, C_12)
  
  #If it is the first iteration, we set the sample mean to our first estimate
  if (k == 1){
    C_12_bar <- C_12
  }
  
  #We now generate our next sample mean and variance
  out <- gen_sample_mean_var(k, C_12, C_12_bar, S_sq)
  
  #We then retrieve these values
  C_12_bar <- out[1]
  S_sq <- out[2]
  
  #We then print this to assess convergence
  #print(sqrt(S_sq/k))
  
  #We then check we have satisfied our requirements for confidence interval, the last condition ensures we     record only the first time we satisfy this requirement
  
  if (sqrt(S_sq/k) < (500/1.645) & k != 1 & (C_12_90+k_90+S_sq_90 == 0)){
    
    #We then collect our output values
    C_12_90 <- C_12_bar
    k_90 <- k
    S_sq_90 <- S_sq
  }
  
  #We then add to counter
  k <- k+1
  
}
```

# Output Analysis

## Estimation of `C_12`

We first want an acceptable d, so we calculate d = (500/1.645), Assuming CLT applies.

Thus, we have we run the loop until:

$$ \frac{S}{\sqrt{k}} < \frac{500}{1.645}$$

where S is the standard deviation up until that iteration, and k is the iteration.

We next estimate the capital we finish with, if we retrieve our output variable C_12

```{r}
C_12_90
k_90
S_sq_90 
```
From here, we calculate our final standard deviation

```{r}
S_90 <- sqrt(S_sq_90/k_90)
S_90
```

So we on the 2538th iteration, we achieved our estimate of 27375.34. Our estimator has a standard deviation of 303.95.

From here, we use the z-score of 1.96 to calculate an interval that we can be 95% our true value is in. With our standard deviation of 303.95, we find calculate 1.96*303.95. So our interval is +/- 595.06.

## Plots

#Distribution Visualisation 

```{r}
freq <- data.frame(list(capital_list))
```

```{r}
plot_1 <- ggplot(freq, aes(x = capital_list)) +
    geom_histogram(bins = 70, fill = "#00BFC4") +
    xlab("Capital Stock at 12 Months") +
    ylab("Simulations") +
    geom_vline(xintercept=30000)

plot_1
```

