---
title: "Client Generation"
output:
  html_document:
    df_print: paged
    toc: yes
---

Contained in this notebook are the generation of the 25 composite clients.

As required we first set the seed to 1.

```{r}
set.seed(1)
```

# Client Generation 

We are required to generate 25 **unique** numbers, drawn uniformly, between 1 and 60. This is done in the chunk below

```{r}
#Initialise an empty vector to hold our numbers
composite_clients <- c()

#Start a while loop that ceases once the quantity of unique numbers reaches 25
while (length(unique(composite_clients)) < 25) {
  
  #Randomly generate a number between 1 and 60
  client <- ceiling(60*runif(1))
  
  #Append this number to the composite_clients list
  composite_clients <- c(composite_clients, client)
}

#Retrieve only the unique entries
composite_clients <- unique(composite_clients)
```

We now manipulate our data for ease of usage in AMPL
```{r}
#Paste c at the start of every entry in composite clients
composite_clients <- paste0("c", composite_clients)
```

We finally write to a csv file for later
```{r}
write.csv(composite_clients, "client_data/clients.csv", row.names = T)
```

# Client Location Retrieval

It will be of use later to have the locations of our composite clients in their own csv files, the next section details this process

```{r}
#We first read in the locations of customers we generated in "1 Warehousing"
c_x <- read.csv("grid_data/c_x.csv")
c_y <- read.csv("grid_data/c_y.csv")

#We then index these locations with the list of composite clients
composite_c_x <- c_x[c_x$X %in% composite_clients, ]
composite_c_y <- c_y[c_y$X %in% composite_clients, ]

#We then write the x and y coordinates to new csvs
write.csv(composite_c_x, "client_data/comp_c_x.csv", row.names = T)
write.csv(composite_c_y, "client_data/comp_c_y.csv", row.names = T)
```

