---
title: "Product Specific Insurance"
output:
  html_document:
    df_print: paged
    toc: yes
---

Contained in this notebook is the product specific insurance simulation

As required, we first set the seed to 0, for re-producability of our results.

```{r}
set.seed(1)
```

# Function Definitions

```{r}
next_pois <- function(t, x) {
  U <- runif(1)
  return(t - (1/x) * log(U)) 
}
```

```{r}
mu_t = function(t){
  return(1/(t+12))
}
```

```{r}
next_dep <- function(t, lambda) {
  flag = 1
  while(flag){
    U1 <- runif(1)
    t = t - (1/lambda) * log(U1)
    
    U2 <- runif(1)
    
    if (U2 <= mu_t(t)/lambda) {
      T_s <- t
      flag = 0
    }
  }
  
  return (T_s)
}
```

```{r}
new_month <- function(t, months) {
  if (floor(t) %in% months) {
    return(FALSE)
  } else {
    return(TRUE)
  }
}
```

# Simulation 

We are first given some parameters, which are initialized below

```{r}
#Monthly poisson process parameter for arrivals
lambda <- 3

#Yearly poisson process parameter for claims
alpha <- 3.5

#Starting capital
c_0 <- 50000

#Capital floor
C <- 30000
  
#Fixed monthly fee
M <- 300
```


```{r}
### Output Variables ################################

#We first define a list which records if the firm went below the threshold C.
B <- c()




### Main Loop ########################################

#We next define a for loop, so we run the simulation for 1000 iterations.

for (k in 1:1000) {
  
### Starting Parameters #################
  
  #Start at time 0
  t <- 0
    
  #Number of arrivals by time t
  n_A <- 0
  
  #Number of departures by time t
  n_D <- 0
  
  #Number of claims by time t
  n_C <- 0
  
  #We run simulation for 12 months
  total_t <- 12
  
### State variables ######################
  
  #Number of customers currently in system
  n_0 <- 0
  
  #Defines our current cost accrued
  cost <- 0
  
  #Defines our current revenue generated
  rev <- 0
  
  #Describes what month we are currently in
  months <- c(0)
  
### Event variables ######################
  
  #Define time of next arrival from Poisson process 
  t_A <- next_pois(t, lambda)
  
  #Define time of next departure
  t_D <- Inf
  
  #Define list of next claims
  t_C <- c(Inf)
  
### 12 Month Loop ########################

  while(t <= total_t){
    
    #Calculate whether we are in new month yet
    if (new_month(t, months)) {
      
      #If yes, then add monthly income to revenue
      months <- c(months, floor(t))
      rev <- rev + M*n_0
    }
    
    #If there is arrival
    if ((t_A <= t_D) & (all(t_A <= t_C))){
      
      #Set time to time of next arrival
      t <- t_A
      
      #Add arrival to number of arrivals
      n_A <- n_A + 1
      
      #Count arrival in system count
      n_0 <- n_0 + 1
      
      #Calculate next arrival time
      t_A <- next_pois(t, lambda)
      
      #On first iteration, we now calculate time to next claim
      t_C[n_A] <- next_pois(t, (alpha/12))
      
      #On first iteration, we need to calculate next departure time
      if (n_A == 1) {
        t_D <- next_dep(t, lambda)
      }
      
    }
    
    #If there is a departure
    else if ((t_D < t_A) & all((t_D < t_C))) {
      
      #Set time to time of next departure
      t <- t_D
      
      #Subtract departure from system count
      n_0 <- n_0 - 1
      
      #Add departure to departure count
      n_D <- n_D + 1
      
      #Calculate next departure
      t_D <- next_dep(t, lambda)
    }
    
    #If there is a claim
    else if (any((t_C < t_A)) & any((t_C < t_D))){
      
      #Set time to time of next claim
      t <- min(t_C)
      
      #Add one claim to claim count
      n_C <- n_C+1
  
      #Generate next claim time
      t_C[which.min(t_C)] <- next_pois(t, (alpha/12))
      
      ##Calculate pay-out 
      
      #Generate random uniform variable
      pay_out_p <- runif(1)
    
      #If the variable is less than 0.6, then execute code
      if (pay_out_p <= 0.6){
        
        #Calculate random variable, multiply by 10, and obtain its upper integer 
        X <- ceiling(10*runif(1))
        
        #Calculate pay-out based on this
        pay_out <- 300*X + 500
        
        #Add it to the running total
        cost <- cost + pay_out
      }
    }
  }
  
  #Checks if they are below the threshold
  if ((c_0 - cost + rev) <= C) {
   
    #If they are, add a 1 to the list
    B <- c(B,1)
  } else{
    
    #If they are not, add a 0 to the list
    B <- c(B,0)
  }
  
}
```

# Output Analysis

## Estimation of `P`

In this section we estimate `P`, that is, the probability of the capital at the end of the 12 months going beneath C

We first examine our output B, we see there is a pretty even distribution of 1s and 0s. 
```{r}
B
```
For an exact answer, we count the number of 1s, which imply a simulation where the company dropped below C, and divide it by the amount of simulations ran.

```{r}
#Count values of 1s, the function stores the 1s count at index 2
value_count <- table(B)

#Calculate P as described above
P <- value_count[2] / length(B)

#Output P
P
```
We observe a probability of 0.523, just above half.



