---
title: "Product Specific Insurance"
output:
  html_document:
    df_print: paged
    toc: yes
---

Contained in this notebook is the product specific insurance simulation

# Setting up

We first import libraries. These are only used for the plots, so it is not necessary for the simulation and extraction of output variables

```{r}
library(ggplot2)
library(dplyr)
```

As required, we first set the seed to 1, for re-producability of our results.

```{r}
set.seed(1)
```


# Function Definitions

We define the following function to generate the next event time after t in a homogeneous Poisson process

```{r}
#The function takes in current time t and intensity x
next_pois <- function(t, x) {
  
  #Generates random uniform variable
  U <- runif(1)
  
  #Returns the next time, following formula for Poisson process
  return(t - (1/x) * log(U)) 
}
```

The next two functions are the building blocks for the non-homogeneous Poisson process. We first define mu_t to calculate the rate of the process, and next_dep generates the next time after t in the process.

```{r}
#The function takes in current time t
mu_t = function(t){
  
  #Calculates intensity using formula given in brief
  return(1/(t+12))
}
```

```{r}
#The function takes in current time t and max possible mu
next_dep <- function(t, mu) {
  
  #Sets flag for the while loop so it runs
  flag = 1
  
  while(flag){
    
    #Generates random uniform variable
    U1 <- runif(1)
    
    #Calculates next event time in process
    t = t - (1/mu) * log(U1)
  
    #Generates a second random uniform variable
    U2 <- runif(1)
    
    #Calculates the rate, and checks if it satisfies requirement for non-homogeneous process
    if (U2 <= mu_t(t)/mu) {
      
      #Sets time to t
      T_s <- t
      
      #Breaks while loop
      flag = 0
    }
  }
  
  #Returns the calculated next event time t
  return (T_s)
}
```

We next define a function that allows us to track which months we are in. The function checks if the month is in our tracking list, and returns true if it inst, and false otherwise.

```{r}
#Takes in current time and current month list
new_month <- function(t, months) {
  
  #If the floor of the current t is not in the months list
  if (floor(t) %in% months) {
    
    #Returns false
    return(FALSE)
    
  } else {
    
    #Returns true 
    return(TRUE)
  }
}
```

# Simulation 

In this section we define our simulation

We are first given some parameters, which are initialized below

```{r}
#Monthly poisson process parameter for arrivals and claims
lambda <- 3

#Monthly non-homogeneous Poisson process rate, since this is the max mu_t can attain
mu <- 1/12

#Yearly poisson process parameter for claims
alpha <- 3.5

#Starting capital
c_0 <- 50000

#Capital floor
C <- 30000
  
#Fixed monthly fee
M <- 300
```


```{r}
### Output Variables ################################

#We first define a list which records if the firm went below the threshold C.
B <- c()




### Main Loop ########################################

#We next define a for loop, so we run the simulation for 1000 iterations.

for (k in 1:1000) {
  
### Variables #################
  
  #Start at time 0
  t <- 0
    
  #Number of arrivals by time t
  n_A <- 0
  
  #We run simulation for 12 months
  total_t <- 12
  
### State variables ###########
  
  #Number of customers currently in system
  n_0 <- 0
  
  #Defines our current cost accrued
  cost <- 0
  
  #Defines our current revenue generated
  rev <- 0
  
  #Describes what month we are currently in
  months <- c(0)
  
### Event variables ###########
  
  #Define time of next arrival from Poisson process 
  t_A <- next_pois(t, lambda)
  
  #Define list of next departures
  t_D <- c(Inf)
  
  #Define list of next claims
  t_C <- c(Inf)
  
### 12 Month Loop ########################

  while(t <= total_t){
    
    #Calculate whether we are in new month yet
    if (new_month(t, months)) {
      
      #If yes, then add month to list
      months <- c(months, floor(t))
      
      #then add monthly income to revenue
      rev <- rev + M*n_0
    }
    
    #If there is arrival
    if ((all(t_A <= t_D)) & (all(t_A <= t_C))){
      
      #Set time to time of next arrival
      t <- t_A
      
      #Add arrival to number of arrivals
      n_A <- n_A + 1
      
      #Count arrival in system count
      n_0 <- n_0 + 1
      
      #Calculate next arrival time
      t_A <- next_pois(t, lambda)
      
      #We calculate time to next claim for this customer
      #We index the list by the number arrival they are
      t_C[n_A] <- next_pois(t, (alpha/12))
      
      #On first iteration, we need to calculate next departure time for this customer
      #We again index list by the number of arrival they are
      t_D[n_A] <- next_dep(t, mu)
      
    }
    
    #If there is a departure
    else if (any(t_D < t_A) & any(t_D < t_C)) {
      
      #Set time to time of next departure
      t <- min(t_D)
      
      #Subtract departure from system count
      n_0 <- n_0 - 1
      
      #Set this customers departure time to infinity, since they have now left
      t_D[which.min(t_D)] <- Inf
      
      #Set this customers next claim time to infinity, since they have now left
      t_C[which.min(t_D)] <- Inf

    }
    
    #If there is a claim
    else if (any((t_C < t_A)) & any((t_C < t_D))){
      
      #Set time to time of next claim
      t <- min(t_C)
  
      #Generate next claim time for this customer
      t_C[which.min(t_C)] <- next_pois(t, (alpha/12))
      
      ## Calculate pay-out ##
      
      #Generate random uniform variable
      pay_out_p <- runif(1)
    
      #If the variable is less than 0.6, then execute code
      if (pay_out_p <= 0.6){
        
        #Calculate random variable, multiply by 10, and obtain its upper integer 
        X <- ceiling(10*runif(1))
        
        #Calculate pay-out based on this
        pay_out <- 300*X + 500
        
        #Add it to the running total
        cost <- cost + pay_out
      }
    }
  }
  
  #Checks if they are below the threshold at the end of iteration
  if ((c_0 - cost + rev) <= C) {
   
    #If they are, add a 1 to the list
    B <- c(B,1)
  } else{
    
    #If they are not, add a 0 to the list
    B <- c(B,0)
  }
}
```

# Output Analysis

## Estimation of `P`

In this section we estimate `P`, that is, the probability of the capital at the end of the 12 months going beneath C

We first examine our output B, we see there is a pretty even distribution of 1s and 0s. 
```{r}
#Prints B
B
```
For an exact answer, we count the number of 1s, which imply a simulation where the company dropped below C, and divide it by the amount of simulations ran.

```{r}
#Count values of 1s, the function stores the 1s count at index 2
value_count <- table(B)

#Calculate P as described above
P <- value_count[2] / length(B)

#Output P
P
```
We observe a probability of 0.384.

# Plots 

To remedy the probability, we now experiment with other values of M

## Bar Plot (M = 300)

We first rename column names to make visualization clearer

```{r}
#Counts how many values of 1s and 0s and renames columns
value_count <- as.data.frame(value_count) %>% rename("Outcome" = B, "Simulations" = Freq)
```

```{r}
#Plots outcome 
plot_1 <- ggplot(data = value_count, aes(x = Outcome, y = Simulations)) +
  
          #Sets bar plot and sets colour
          geom_bar(stat = 'identity', fill = "#00BFC4") +
  
          #Renames axes
          scale_x_discrete(labels=c("0" = "Above Threshold", "1" = "Below Threshold"))

#Outputs plot
plot_1
```
## Bar Plot (M=400)

Probability of legal issues = 0.069

```{r}
#Counts how many values of 1s and 0s and renames columns
value_count <- as.data.frame(value_count) %>% rename("Outcome" = B, "Simulations" = Freq)
```

```{r}
#Plots outcome
plot_2 <- ggplot(data = value_count, aes(x = Outcome, y = Simulations)) +
  
          #Sets bar plot and sets colour
          geom_bar(stat = 'identity', fill = "#00BFC4") +
  
          #Renames axes
          scale_x_discrete(labels=c("0" = "Above Threshold", "1" = "Below Threshold"))

#Prints plot
plot_2
```


## Bar Plot (M=350)

Probability of legal issues = 0.189

```{r}
#Counts how many values of 1s and 0s and renames columns
value_count <- as.data.frame(value_count) %>% rename("Outcome" = B, "Simulations" = Freq)
```

```{r}
plot_3 <- ggplot(data = value_count, aes(x = Outcome, y = Simulations)) +
  
          #Sets barplot and changes color
          geom_bar(stat = 'identity', fill = "#00BFC4") +
  
          #Renames axes
          scale_x_discrete(labels=c("0" = "Above Threshold", "1" = "Below Threshold"))

#Prints plot
plot_3
```



