---
title: "Grid Generation"
output:
  html_document:
    df_print: paged
    toc: yes
---

Contained in this notebook is the code used for generating the grid of potential locations, and clients.

As requested, we first set the set to 1, this allows reproducability in our code

```{r}
set.seed(1)
```

# Grid Generation

We operate on a grid of [-10,10] x [-10,10], which means there are 21^2 potential points. As such, we wish to generate a matrix of 15 random "f"s (to represent facilities), and 60 random "c"s (to represent customers). 


```{r}
#Define p to be the height and width of the grid
p<-21

#Define n_f to be the number of potential facilities, n_c to be number of customers
n_f <- 15
n_c <- 60

#Define 20^2 uniform random variables, in a 21x21 matrix
unif_grid <- matrix(runif(p^2), nrow = p, ncol = p)

#Define a vector of zeros, of length 21^2
grid <- numeric(p^2)

#Sort the matrix of the uniform variables, and set the top 15 variables indexes equal to f in the grid of zeros 
grid[order(unif_grid, decreasing = TRUE)[1:n_f]] <- "f"

#Sort the matrix of the uniform variables, and set the next top 60 variables indexes equal to c in the grid of zeros
grid[order(unif_grid, decreasing = TRUE)[(n_f+1):(n_c+n_f)]] <- "c"

#Reshape grid to be a 20x20 matrix
grid <- data.frame(matrix(grid, nrow = p, ncol = p))

#Output grid
grid
```

We now prove that we have satisfied the requirements

```{r}
#Sum up and output all instances of 1 in the grid
num_ones <- sum(grid == "f")
num_ones

#Sum up and output all instances of 2 in the grid
num_twos <- sum(grid == "c")
num_twos
```
As we have 15 "f"s, and 60 "c"'s we have satisfied the requirements.

For ease of use later, we will rename the column names to represent the coordinates.

```{r}
#Rename columns from -10 to 10 inclusive
colnames(grid) <- paste0(-10:10)

#Rename rows from -10 to 10 inclusive
row.names(grid) <- paste0(-10:10)

grid
```

# Writing our grid

## The grid

We write our grid to a file that we can access later. The file is called grid.csv

```{r}
#Write the grid to csv file
write.csv(grid, "grid_data/grid.csv", row.names=T)
```

## Customer Coordinates 

We also write a list of x coordinates and y coordinates for each customer, for ease of use in AMPL.

```{r}
#We first extract the indices of the grid that are equal to "c"
c_ind <- which(grid == "c", arr.ind = T)

#From the indices, we extract the corresponding row and column names
c_x <- row.names(grid)[c_ind[,1]]
c_y <- colnames(grid)[c_ind[,2]]

#Merge these two vectors into a dataframe
c_coords <- data.frame(c_x, c_y)

#We rename the rows "c" suffixed by a number 1 to 60, for identification in AMPL
row.names(c_coords) <- paste0("c", 1:60)

#We rename the columns x and y to represent coordinates
colnames(c_coords) <- c("x", "y")

#Write the corresponding columns to csv files
write.csv(c_coords[,"x"], "grid_data/c_x.csv", row.names=row.names(c_coords))
write.csv(c_coords[,"y"], "grid_data/c_y.csv", row.names=row.names(c_coords))
```


## Facility Coordinates

We also write a list of x coordinates and y coordinates for each customer, for ease of use in AMPL.

```{r}
#We first extract the indices of the grid that are equal to "f"
f_ind <- which(grid == "f", arr.ind = TRUE)

#From the indices, we extract the corresponding row and column names
f_x <- row.names(grid)[f_ind[,1]]
f_y <- colnames(grid)[f_ind[,2]]

#Merge these two vectors into a dataframe
f_coords <- data.frame(f_x, f_y)

#We rename the rows "f" suffixed by a number 1 to 60, for identification in AMPL
row.names(f_coords) <- paste0("f", 1:15)

#We rename the columns x and y to represent coordinates
colnames(f_coords) <- c("x", "y")

#Write the corresponding columns to csv files
write.csv(f_coords[,"x"], "grid_data/f_x.csv", row.names=row.names(f_coords))
write.csv(f_coords[,"y"], "grid_data/f_y.csv", row.names=row.names(f_coords))
```

