---
title: "Grid Generation"
output:
  html_document:
    df_print: paged
    toc: yes
---

Contained in this notebook is the code used for generating the grid of potential locations, and clients.


#Setting up

As requested, we first set the set to 1, this allows reproducability in our code

```{r}
set.seed(1)
```

# Grid Generation

We operate on a grid of [-10,10] x [-10,10], so we can generate random variables and transform them as necessary. Specifically, we multiply them by 20 and minus 10.

```{r}
#Number of facilities
n_f <- 15

#Number of customers
n_c <- 60

#Generate the facilities as described, and put them into dataframe
f_y <- data.frame(round(20*runif(n_f) - 10,2))
f_x <- data.frame(round(20*runif(n_f) - 10,2))

#Generate the customers as described, and put them into dataframe
c_y <- data.frame(round(20*runif(n_c) - 10,2))
c_x <- data.frame(round(20*runif(n_c) - 10,2))
```

We now rename the rows for easier use in AMPL.

```{r}
#Prefix the row numbers with f, to indicate facility
row.names(f_y) <- paste0("f", 1:n_f)
row.names(f_x) <- paste0("f", 1:n_f)

#Prefix the row numbers with c, to indicate customer
row.names(c_y) <- paste0("c", 1:n_c)
row.names(c_x) <- paste0("c", 1:n_c)
```

# Writing our grid

## The grid

## Customer Coordinates 

We write a list of x coordinates and y coordinates for each customer, for ease of use in AMPL.

```{r}
#Write the corresponding columns to csv files
write.csv(c_x, "grid_data/c_x.csv", row.names=row.names(c_x))
write.csv(c_y, "grid_data/c_y.csv", row.names=row.names(c_y))
```


## Facility Coordinates

We write a list of x coordinates and y coordinates for each customer, for ease of use in AMPL.

```{r}
#Write the corresponding columns to csv files
write.csv(f_x, "grid_data/f_x.csv", row.names=row.names(f_x))
write.csv(f_y, "grid_data/f_y.csv", row.names=row.names(f_y))
```

